Tournaments

### 2024-10-18 paper.qmd
Added to library

---
title: "Tournaments"
author: "Greg"
format: html
editor: visual
---

@@

 - Heat based events (Track 5000m and below, swimming, )

@@

>>>>

---
title: "Tournaments"
author: "Greg, Josie, Zach, Ryan"
format: html
editor: visual
---

Llull (1283)

Kendall and Smith (1940): Judges makes consistent preferences.

Slater's I (1961): Measure of inconsistency

Thurstone Mosteller model (1928): Bradley Terry Model with a normal CDF transformation.

Kendall-Wei (1952)
Elo (1978)
Glicko (1998) and Glicko2 (2006?): Essentially Bayesian Elo.  
Trueskill (2006): Used in halo 2 or 3.

Weak stochastic probablity. $P(A \rightarrow B) > 0.5$  and $P(B \rightarrow C) > 0.5$ then $P(A \rightarrow C) > 0.5$.

CRSP: Chain Rock Scissor Paper.  Non transitive model.

Ratings vs rankings: Ratings are numeric estimates of strengths.  Rankings are a function of ratings.

Let's start with what a BAD tournament would be.

Quarto manuscript template:https://github.com/mikemahoney218/quarto-arxiv

##Papers

https://www.sciencedirect.com/science/article/pii/S0378375803003215
"Maximum weight perfect match problem"

## Deterministic Binary Outcome Tournaments

 - Knockout (KO) lKO
  - 1KO
  - 2KO
      - True 3rd, college wrestling, repechage
  - 3KO
  - Seeding issues,.

 - nRR 
  - 1RR
  - 2RR
  - partial RR

## Dynamic Binary Outcome Tournaments

  - Swiss
  - Dynamic Knockout (reseeding after every round)

@@

 - Heat based events (Track 5000m and below, swimming)

@@

Note for Greg: 
Can we build a simulator that computes the probability of a team winning in two steps: 1) the team strength comes from a distribution itself and then the actual outcome come from flipping a coin based on the particular draw of the distribtuion.

Can we model a sport and how muhc variability it has?  So like estimate the probability of rteam A beating team B as a function of relative strengths but also use that other distribution to model the variability of the sport.  Does this exist?
